Mixture-of-interests models for representing users with diverse interests

### 2017-11-04 paper/paper.tex
Add dataset stats table.
Improve table automation.

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{commath}
\usepackage{threeparttable}

@@

@@

\subsection{Hyperparameter search}
Figure~\ref{fig:hyper} plots the maximum test MRR obtained by each of our algorithms as a function of the number of elapsed hyperparameter search iterations.

\begin{table}[htbp]
\begin{threeparttable}
\caption{Experimental results}
\label{tb:results}
\begin{tabular}{lrrr}
\toprule
 Model               &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
 LSTM                &          0.0901 &   0.1502 &          0.1158 \\
 Mixture-LSTM        &          0.0999 &   0.1889 &          0.1358 \\
 Linear Mixture-LSTM &          0.0000 &   0.1484 &          0.1163 \\
 \midrule
 Bilinear            &          0.0999 &   0.1001 &          0.0738 \\
 Projection Mixture  &          0.0983 &   0.0698 &          0.0712 \\
 Embedding Mixture   &          0.0952 &   0.1696 &          0.0853 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond: how many items can be scored per millisecond
\item[3] Ratio of binary PPMS to real-valued PPMS
\item[4] Ratio of memory required to store binary vs. real-valued parameters
}
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}
\caption{Effect of number of mixture components}
\label{tab:nummixtures}
\begin{subtable}{\columnwidth}
\caption{Sequence models}
\begin{tabular}{rrrr}
\toprule
   Components &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
                    2 &          0.0921 &   0.1538 &          0.1262 \\
                    4 &          0.0999 &   0.1689 &          0.1304 \\
                    6 &          0.0991 &   0.1889 &          0.1358 \\
                    8 &          0.0982 &   0.1865 &          0.1327 \\
\bottomrule
\end{tabular}
\end{subtable}
\begin{subtable}{\columnwidth}
\caption{Factorization models}
\begin{tabular}{rrrr}
\toprule
   Components &   Movielens 10M &   Amazon &   Goodbooks-10K \\
\midrule
                    2 &          0.0952 &   0.1343 &          0.0797 \\
                    4 &          0.0952 &   0.1583 &          0.0840 \\
                    6 &          0.0913 &   0.1612 &          0.0811 \\
                    8 &          0.0907 &   0.1696 &          0.0853 \\
\bottomrule
\end{tabular}
\end{subtable}\end{table}

\begin{figure*}[h]
  \caption{Hyperparameter search}
  \label{fig:hyper}
  \includegraphics[width=0.8\textwidth]{hyperparam_search.eps}
\end{figure*}

>>>>

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{commath}
\usepackage{threeparttable}
\usepackage{caption}

@@

\begin{table}
  \caption{Dataset statistics}
  \label{tab:datasets}
  \input{includes/datasets.tex}
\end{table}

@@

\subsection{Hyperparameter search}
Figure~\ref{fig:hyper} plots the maximum test MRR achieved by each algorithm as a function of the number of elapsed hyperparameter search iterations. Both baseline and mixture models benefit from hyperparameter tuning. All algorithms converge to their optimum performance relatively quickly, suggesting a degree of robustness to hyperparameter choices. Mixture-LSTM and Embedding Mixture models quickly outperform their baseline counterparts, and maintain a stable performance lead thereafter. This lends support to our belief that the mixture models' superior accuracy reflects their greater capacity to model the recommendation problem well, rather than being an artifact of the experimental procedure or researcher bias.

\subsection{Number of taste components}
We summarize the effect of increasing the number of taste mixture components in Table~\ref{tab:nummixtures}. By and large, there is a dose-response relationship between the number of mixtures and recommendation quality: being able to represents more distinct user tasts yields better results.

\begin{table}[htbp]
\begin{threeparttable}
\caption{Experimental results}
\label{tb:results}
\input{includes/performance.tex}
\begin{tablenotes}
\small{
\item[1] Ratio of binary model MRR to real-valued model MRR
\item[2] Predictions Per Millisecond: how many items can be scored per millisecond
\item[3] Ratio of binary PPMS to real-valued PPMS
\item[4] Ratio of memory required to store binary vs. real-valued parameters
}
\end{tablenotes}
\end{threeparttable}
\end{table}

\input{includes/hyperparameters.tex}

\begin{figure*}[h]
  \captionsetup{width=.8\linewidth}
  \caption{Maximum test MRR vs number of hyperparameter search iterations. Sequence-based models in the top row; factorization-based models in the bottom row.}
  \label{fig:hyper}
  \includegraphics[width=0.8\textwidth]{includes/hyperparam_search.pdf}
\end{figure*}
